wind_diagrams

### 2019-12-17 wind_analyses.Rmd
update

              paddle=FALSE, type="station", width=2))
)
# png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose
# ?plot
```

match_func <- function(df){
  match <- df  %>%  
  left_join(wind_months, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
wind_months <- site_list_sub %>% 
  left_join(wind_months)

wind_match_SACTN <- match_func(df = SACTN_US)

load("Data/OISST.RData") # 2 decimal places
OISST <- BC_avhrr_only_v2_Document_Document

match_func <- function(df){
  match <- df  %>%  
  left_join(wind_months, by = c("lat", "date", "lon")) %>% 
  na.trim()
  return(match)
}
wind_match_OISST <- match_func(df = OISST)

wind_renamed <- wind_match %>% 
  mutate(dir_circ = ifelse(dir_circ < 0, dir_circ+360, dir_circ)) %>%
  dplyr::rename(spd = mean_speed) %>%
  dplyr::rename(dir = dir_circ) %>% 
  filter(spd > 0)

Are there more SE winds in summer, but come later in January? i.e any changes in SE wind and changes in water temperature
To answer this first question we will take total counts of SE winds (180 - 270 degrees) for each year and counts for just summer (Jan - Mar). We will also take counts of each Summer month individually to see what the long-term trends are. Once we've pinned down any trends we will look at the same temporal agregations for temperatures to see what those trends are. With all of that determined we can then see what the relationship between the two is.

```{r}
# First filter out only the SE data
SE_renamed <- wind_renamed %>% 
  filter(dir >= 180, dir <= 270)

# Then create diifferent temporal results
SE_annual <- SE_renamed %>% 
  group_by(site, year) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
SE_summer <- SE_renamed %>% 
  filter(season == "Summer") %>% 
  group_by(site, year, season) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
SE_monthly <- SE_renamed %>% 
  filter(season == "Summer") %>% 
  group_by(site, year, season, month) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
# Plots
## Annual count of SE wind
ggplot(data = SE_annual, aes(x = year, y = count)) +
  geom_line() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)
## Annual count of SE wind in Summer
### The trends between annual and summer SE wind counts are remarkably similar
ggplot(data = SE_summer, aes(x = year, y = count)) +
  geom_line() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)
## Summer month count of SE winds
ggplot(data = SE_monthly, aes(x = year, y = count)) +
  geom_line(aes(colour = month)) +
  geom_smooth(aes(colour = month), method = "lm") +
  facet_wrap(~site)
# March SE winds have been increasing in count in Hout Bay, Lamberts Bay, and Sea Point
# Feb winds are increasing faster in count in Saldanha Bay
# All SE summer winds are decreasing in Port Nolloth
```

```{r}
# Now having had a look at the data it appears there may be some relationships between SE wind and temperature
# at Sea Point, and perhaps a negative relationship atPort Nolloth

# This outputs the slope of the relationship and the correlation between
# annual count of SE winds mean temperature 
slope_calc <- function(df){
  df %>% 
    mutate(row_num = 1:n()) %>% 
    do(mod1 = lm(count ~ row_num, data = .),
       mod2 = lm(mean_temp ~ row_num, data = .),
       mod3 = lm(mean_temp ~ count, data = .),
       mod4 = cor(.$mean_temp, .$count, method = "pearson", use = "complete.obs")[1]) %>% 
    mutate(wind_slope = summary(mod1)$coeff[2],
           temp_slope = summary(mod2)$coeff[2],
           temp_wind_slope = summary(mod3)$coeff[2],
           temp_wind_r = mod4[1],
           temp_wind_r2 = glance(mod3)$adj.r.squared) %>%
    select(-mod1, -mod2, -mod3, -mod4) %>% 
    mutate_if(is.numeric, round, 2)
}
# glance(lm(mean_temp ~ count, data = SE_annual))

SE_annual %>% 
  group_by(site) %>% 
  slope_calc()
# Summer stats
SE_summer %>% 
  group_by(site, season) %>% 
  slope_calc()
# Monthly summer stats
SE_monthly %>% 
  group_by(site, season, month) %>% 
  slope_calc()

# There's a little something at Hout Bay, not much otherwise
```

Matching the OISST Data and CMC data to match the SACTN dataset

@@

>>>>

              paddle=FALSE, type="station", width=2))
)
# png("Figures/wind.png", width = 8, height = 5, pointsize = 6)
?windRose
# ?plot
```
Matching the OISST Data and CMC data to match the SACTN dataset

@@

match_func <- function(df){
  match <- df  %>%  
  left_join(wind_months, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
# wind_months <- site_list_sub %>% 
#   left_join(wind_months)

wind_match_SACTN <- match_func(df = SACTN_US)
wind_match_OISST <- match_func(df = OISST_final)
wind_match_CMC <- match_func(df = CMC_final)
```

wind_renamed_func <- function(df){
  wind_renamed <- df %>% 
    mutate(dir_circ = ifelse(dir_circ < 0, dir_circ+360, dir_circ)) %>%
    dplyr::rename(spd = mean_speed) %>%
    dplyr::rename(dir = dir_circ) %>% 
    filter(spd > 0)
}

wind_renamed_SACTN <- wind_renamed_func(df = wind_match_SACTN)
wind_renmed_OISST <- wind_renamed_func(df = wind_match_OISST)
wind_renamed_CMC <- wind_renamed_func(df = wind_match_CMC)

```{r}
# First filter out only the SE data
SE_renamed <- wind_renamed %>% 
  filter(dir >= 180, dir <= 270)
# Then create diifferent temporal results
SE_annual <- SE_renamed %>% 
  group_by(site, year) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
SE_summer <- SE_renamed %>% 
  filter(season == "Summer") %>% 
  group_by(site, year, season) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
SE_monthly <- SE_renamed %>% 
  filter(season == "Summer") %>% 
  group_by(site, year, season, month) %>% 
  summarise(count = n(),
            mean_dir = mean(dir, na.rm = T),
            mean_temp = mean(temp, na.rm = T))
# Plots
## Annual count of SE wind
ggplot(data = SE_annual, aes(x = year, y = count)) +
  geom_line() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)
## Annual count of SE wind in Summer
### The trends between annual and summer SE wind counts are remarkably similar
ggplot(data = SE_summer, aes(x = year, y = count)) +
  geom_line() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)
## Summer month count of SE winds
ggplot(data = SE_monthly, aes(x = year, y = count)) +
  geom_line(aes(colour = month)) +
  geom_smooth(aes(colour = month), method = "lm") +
  facet_wrap(~site)
# March SE winds have been increasing in count in Hout Bay, Lamberts Bay, and Sea Point
# Feb winds are increasing faster in count in Saldanha Bay
# All SE summer winds are decreasing in Port Nolloth
```

```{r}
# Now having had a look at the data it appears there may be some relationships between SE wind and temperature
# at Sea Point, and perhaps a negative relationship atPort Nolloth
# This outputs the slope of the relationship and the correlation between
# annual count of SE winds mean temperature 
slope_calc <- function(df){
  df %>% 
    mutate(row_num = 1:n()) %>% 
    do(mod1 = lm(count ~ row_num, data = .),
       mod2 = lm(mean_temp ~ row_num, data = .),
       mod3 = lm(mean_temp ~ count, data = .),
       mod4 = cor(.$mean_temp, .$count, method = "pearson", use = "complete.obs")[1]) %>% 
    mutate(wind_slope = summary(mod1)$coeff[2],
           temp_slope = summary(mod2)$coeff[2],
           temp_wind_slope = summary(mod3)$coeff[2],
           temp_wind_r = mod4[1],
           temp_wind_r2 = glance(mod3)$adj.r.squared) %>%
    select(-mod1, -mod2, -mod3, -mod4) %>% 
    mutate_if(is.numeric, round, 2)
}
# glance(lm(mean_temp ~ count, data = SE_annual))
SE_annual %>% 
  group_by(site) %>% 
  slope_calc()
# Summer stats
SE_summer %>% 
  group_by(site, season) %>% 
  slope_calc()
# Monthly summer stats
SE_monthly %>% 
  group_by(site, season, month) %>% 
  slope_calc()
# There's a little something at Hout Bay, not much otherwise
```
